method

### 2021-12-06 06_Paper/ER-ED/method.Rmd
added ANOVAS vor arousal and effort

# ANOVA subjective arousal ratings
# View Condition

@@

@@

aov.effort = afex::aov_ez(id = "ID",
                          dv = "effort",
                          data = data_ER,
                          within = "block",
                          fun_aggregate = mean)
afex::nice(aov.effort, es = "pes")

>>>>

# ANOVA subjective arousal ratings
# View condition

@@

# View neg and regulate conditions

arousal_Reg = data_ER %>%
  subset(data_ER$block != "view_neu" & data_ER$block != "choice")

aov_arousalReg = afex::aov_ez(id = "ID",
                              dv = "arousal",
                              data = arousal_Reg,
                              within = "block",
                              fun_aggregate = mean)
afex::nice(aov_arousalReg, es = "pes")

# compute posthoc tests for within measures
posthoc_arousalReg = emmeans::emmeans(aov_arousalReg$aov, specs = "block")
pairs(posthoc_arousalReg, adjust = "bonferroni")

@@

effort_Reg = data_ER %>%
  subset(data_ER$block != "view_neu" & data_ER$block != "choice")

aov.effort = afex::aov_ez(id = "ID",
                          dv = "effort",
                          data = effort_Reg,
                          within = "block",
                          fun_aggregate = mean)
afex::nice(aov.effort, es = "pes")
